---
output: github_document
---

# Changing-State Irrelevant Speech Disrupts Visual-Verbal but not Visual-Spatial Serial Recall

John E. Marsh, Mark J. Hurlstone, Alexandre Marois, Linden J. Ball, Stuart B. Moore, François Vachon, Sabine J. Schlittmeier, Jan Philipp Röer, Axel Buchner, Frederik Aust, & Raoul Bell

---

```{r}
#| label: setup
#| echo: false

library("targets")
knitr::opts_chunk$set(echo = FALSE)
```

This repository contains research products associated with the publication.

The `data_raw` directory contains the data in CSV format; RData-files can be found in `data_processed/`.

The analyses herein were performed with the R package [**targets**](https://cran.r-project.org/web/packages/targets/index.html) and can be rerun by executing the file `_make.sh`.
*Note that rerunning the analyses may take several days (see below).*
The analyses are run separately for each study and the results are stored in the directories `mochasta1/_targets/` and `mochasta2/_targets/`.
To run the analysis for Experiment 1 set the `project` variable in `_make.sh` to `mochasta1` (and analogously for Experiment 2).

The Quarto files in the directories `mochasta1` and `mochasta2` create reports of the results of the analyses reported in the paper.

The Bayesian meta-analysis reported in the paper was performed by hand using the online [Bayes factor calculator](https://users.sussex.ac.uk/~dienes/inference/Bayes.htm) by Zoltan Dienes; hence, no code is provided for this analysis.

## Preferred citation

```{r}
#| label: citation
#| echo: false
#| comment: ""

cffr::cff_to_bibtex(x = "CITATION.cff") |>
  toBibtex()
```

## Software requirements

The version of R and all packages required to reproduce the anlysis are listed in the `DESCRIPTION` file.
Additonally, it is required to install the **mochasta** package from this GitHub repository.

```{r}
#| label: install
#| echo: true
#| eval: false

# Install the mochasta package from GitHub
remotes::install_github("crsh/mochasta")

# Install from a local copy of the repository
devtools::install("path/to/mochasta")
```


## Computational requirements

Running all analyses may take severa on a Desktop computer even when Bayesian models are fit in parallel on 7 cores (current setting).
To control the number of cores used for parallel processing, change the **targets** `controller` option in `targets.r` in the folders for each experiment. 

### Experiment 1

```{r}
#| include: false

mochasta1_diagram <- tar_mermaid(
  label = c("time", "branches")
  , script = "./mochasta1/results/targets.r"
  , store = "./mochasta1/results/_targets"
  , reporter = "silent"
)

mochasta2_diagram <- tar_mermaid(
  label = c("time", "branches")
  , script = "./mochasta2/results/targets.r"
  , store = "./mochasta2/results/_targets"
  , reporter = "silent"
)
```

```{r}
#| label: mochasta1-dependencies
#| results: asis

cat("```mermaid\n")
cat(mochasta1_diagram, sep = "\n")
cat("\n```")
```

### Experiment 2

```{r}
#| label: mochasta2-dependencies
#| results: asis

cat("```mermaid\n")
cat(mochasta2_diagram, sep = "\n")
cat("\n```")
```
